%As a volunteer for caring autism teenagers, my close encounter with them led to my interest in \textit{Social Computing}. 
%Autism reduces social awareness and language abilities, 
%making it hard to emotionally connect with the sufferer through normal communication channels.
%Online interaction offers an alternative approach to bridge their social gaps.
%During the volunteer days, I was impressed by the active social characteristics of several autism teenagers online,
%which is just opposite to their behaviors in reality.
%One of the most impressive experiences is an online conversation between me and a high-functional autism boy,
%who hardly responsed in face-to-face interaction.
%I was surprised that he actively opened an online chat with me to invite me to take a picnic with him and his family.
%Although his words were ill organized, a positive personality was conveyed via typed messages.
%The mediation of computers turns our communication into a channel which is more perceptable.\\
%
%\noindent
%Witnessing the effect of the Internet on the boy, I asked myself:
%``how to help humankind apply to and live better with cyber communication channel?''
%Similar changes are not unique to special groups but are encountered routinely in daily life,
%such as one's hyperpersonality online.
%Technology has extended the social space from reality to virtual world.
%People now can open social interaction in any time and any places, overcoming the temporal and spatial obstacles.
%With the increasing growing rate of the Internet and technologies, I believe that in the following decades, 
%\textit{Social Computing} will remain an important research domain under \textit{Human-Computer Interaction} (\acr{HCI}),
%especially \textit{Computer-Mediated Communication}, \textit{Cross-culture Online Interaction}, and \textit{Crowdsourcing}.
%I want to develop emerging technologies mediating social interactions and stimulates the potential power of crowds. 
%Ultimately, I aim to continue my research in academy and nourish future stars after pursuing PhD.\\

\noindent
My interest in Human-Computer Interaction (\acr{HCI}), especially the Social Computing aspect 
was motivated by my volunteering experience in accompnaying and taking care of Autistic teenagers in StarRain Association in Taipei. 
Autism reduces individual's social awareness and communication ability, 
making it hard to emotionally connect with the sufferer using common communication channels such as language. 
And I observe that online interaction offers an alternative way of communication that empowers these autistic teenagers. 
One of the most impressive experiences is an online conversation between me and a high-functional autism boy, 
who hardly responsed in face-to-face interaction. 
I was surprised that he actively opened an online chat with me to invite me to take a picnic with him and his family. 
Although his words were ill-structured, a warm personality was sitll conveyed via typed messages.\\ 

\noindent
Certainly, the impact of computer mediation is not limited to the special group, 
but also prevalent in everyday life and work. 
I have been greatly fascinated by computer-mediated human-human interaction and the value that HCI design in this space may bring to people. 
In particular, I have tremendous interest in topics of 
\emph{computer-mediated communication}, \emph{cross-cultural online interaction}, and \emph{crowdsourcing}. 
I want to develop emerging technologies for mediating social interactions and stimulates the potential power of crowds. 
Ultimately, I aim to continue my research in academics and to contribute to the education of HCI and Social Computing after PhD.\\

























