%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt, a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions
\usepackage{indentfirst}

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Joey Chiao-Yin Hsiao}{}  % Your name and date of birth or subtitle

\noindent\href{mailto:joeycyhsiao@gmail.com}{joeycyhsiao@gmail.com}\bull % Your email address
\textsmaller{+}886 912-697122\bull % Your phone number(s) and Skype username
\href{http://www.joeyhsiao.info}{http://www.joeyhsiao.info}\\ % Your URL
172 Jiande St., East Dist., Taichung, Taiwan 40148\\ 
Applying To: Ph.D. in Technology and Social Behaviors Fall 2015, Northwestern University 

\spacedhrule{1.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	RESEARCH STATEMNET
%----------------------------------------------------------------------------------------

%\roottitle{RESEARCH STATEMENT} % Root section title
%My research...\\
%is very\\
%interesting.

%\spacedhrule{1.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after


%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST
%----------------------------------------------------------------------------------------

\roottitle{RESEARCH INTEREST} % Root section title
Main: Human-Computer Interaction (\acr{HCI}), Computer-Supported Cooperative Work (\acr{CSCW}) 

Sub: Computer-Mediated Communication, Human Computation, Intelligent User Interface

\spacedhrule{1.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\roottitle{EDUCATION} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.ntu.edu.tw}{National Taiwan University}}
{Taipei, Taiwan}
{\headedsubsection % Job title entry for the current employer
	{M.S. in Computer Science}
	{Sep '10 -- Jun '13}
	{\bodytext{Advisor: Dr. Jane Yung-Jen Hsu}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.cmu.edu/silicon-valley/}{Carnegie Mellon University Silicon Valley}}
{Moffett Field (\acr{CA}), \acr{USA}}
{\headedsubsection % Job title entry for the current employer
	{Visiting Student}
	{Jul '12 -- Sep '12} 
	{\bodytext{Advisor: Dr. Ted Selker}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.ntu.edu.tw}{National Taiwan University}}
{Taipei, Taiwan}
{\headedsubsection % Job title entry for the current employer
	{B.S. in Computer Science}
	{Sep '06 -- Jun '10} 
	{\bodytext{}}
}

\spacedhrule{0.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{PUBLICATION} % Top level section

\begin{itemize}

\itemsep=3pt

\item Rajan, R., \textbf{Hsiao, C.-Y.}, Lahoti, D., and Selker, T. 
``Roger that!'' - The Value of Adding Social Feedback in Audio-mediated Communications. 
In \textit{Proc. of \href{http://www.interact2013.org/}{IFIP TC.13 International Conference on Human-Computer Interaction (INTERACT) '13}}, 471-488.
\item Tsai, W.-C. \textbf{Hsiao, C.-Y.}, Lee, H.-C., Huang, H.-C., Hu, J.-C., Liang, R.-H., and Hsu, Y.-J. 
Designing a Reminiscence Aid in Personal Soundscape. 
In \textit{Proc. of \href{http://www.iasdr2013.jp/}{International Association of Societies of Design Research (IASDR) '13}}, 5150-5160.
\item Tsai, W.-C., Lee, H.-C., \textbf{Hsiao, C.-Y.}, Liang, R.-H., and Hsu, Y.-J. 
Framing Design of Reminiscence Aids with Transactive Memory Theory. 
In \textit{\href{http://chi2013.acm.org/}{The ACM SIGCHI Conference on Human Factors in Computing Systems (CHI) '13, Extended Abstracts}}, 331-336.
\item \textbf{Hsiao, C.-Y.}, Jih, W.-R., and Hsu, Y.-J. 
Recognizing Continuous Social Engagement Level in Dyadic Conversation by Using Turn-taking and Speech Emotion Patterns. 
In \textit{\href{http://activitycontext.org/aaai12-archive/aaai12/}{AAAI '12 Activity Context Representation (ACR) Workshop}}.
\item Tsai, W.-C., \textbf{Hsiao, C.-Y.}, Lee, H.-C., Huang, C.-H., and Hsu, Y.-J. 
In Search of Lost Sounds: Designing a Reminiscence Aid in Everyday Soundscape. 
In \textit{Proc. of \textit{\href{http://www.dis2012.org/}{The ACM conference on Designing Interactive Systems (DIS) '12}}}. \\

\textbf{Unpublished Technical Report}
\item \textbf{Hsiao, C.-Y.}, Wang, H.-C., and Hsu, Y.-J. 
The Price of the Priceless: Exploring Perceived Monetary Value and Cost in Friendsourcing.
Submitted to \textit{\href{http://cscw.acm.org/2015/index.php}
{The ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW) '15}} (under review).
\item Huang, D.-Y., \textbf{Hsiao, C.-Y.}, Chan, L., Yeh, Y.-T., Chen, B.-Y., and Hung, Y.-P.
Face-Centric Touch Interface: A Functional and Memorable Input Space with Rich Affordances and Semantics. 
Submitted to \textit{\href{http://chi2015.acm.org/}{The ACM SIGCHI Conference on Human Factors in Computing Systems (CHI) '15}} (under review).
\item \textbf{Hsiao, C.-Y.} Assessing Engagement in Conversation by Hierarchically Decomposing Emotion and Interaction. 
Master's Thesis, Dept. of Computer Science and Information Engineering (\acr{CSIE}), Natl Taiwan Univ.

\end{itemize}

\spacedhrule{0.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after


%----------------------------------------------------------------------------------------
%	HONOR
%----------------------------------------------------------------------------------------

\roottitle{HONOR} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.csie.ntu.edu.tw}{Dept. CSIE}, \href{http://www.ntu.edu.tw}{Natl. Taiwan Univ.}}
{Taipei, Taiwan}
{
	\headedsubsection % Job title entry for the current employer
	{Graduation Representative}
	{Jun '12} 
	{\bodytext{Give a speech in the graduation ceremony as the representative of CSIE master students of 2010}}

	\headedsubsection % Job title entry for the current employer
	{Grade Representative}
	{Sep '07 -- Jun '08} 
	{\bodytext{Bridge students with professors and officers as the representative of CSIE undergraduate of 2006}}

}



%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------

\spacedhrule{5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after
%\spacedhrule{5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after
\roottitle{PROFESSIONAL EXPERIENCE} % Top level section

%--- Intel-NTU ----------------------------------------------------------------------------------------------------------%

\headedsection
{UX Team, \href{http://ccc.ntu.edu.tw/}{Intel-NTU Connected Context Computing Center}}
{Taipei, Taiwan}{

	\headedsubsection
	{Research Assistant}
	{Jul '14 -- Present}
	{\bodytext{Research on user experience and natural user interface under smart environment
			   as the only M.S. researcher in the team}}
}

%--- CSC Lab ----------------------------------------------------------------------------------------------------------%

\headedsection
{\href{http://csclab.tw/}{Collaborative \& Social Computing Lab},
 \href{http://www.cs.nthu.edu.tw}{Dept. CS},
 \href{http://www.nthu.edu.tw}{Natl. Tsing-Hua Univ.}}
{Hsinchu, Taiwan}{

	\headedsubsection
	{Collaborative Researcher}
	{Jul '14 -- Present}
	{\bodytext{Conduct research on friendsourcing, leading a project of devloping a social-driven proofreading system}}
}

%--- ROC Army ----------------------------------------------------------------------------------------------------------%

\headedsection
{Taiwan Army (Mandatory Military Service)}
{Taoyuan, Taiwan}{

	\headedsubsection
	{Human Resources Management System Designer}
	{Jun '14 -- Jul '14}
	{\bodytext{Manage a project of revising military human resources management system in a 4-member team}}

	\headedsubsection
	{Company Chief Consultant (Second Lieutenant)}
	{Aug '13 -- Jun '14}
	{\bodytext{Handle psychological consulting, human resources management, and welfare of a military company with 40+ members}}

}

%--- OpenHCI ----------------------------------------------------------------------------------------------------------%
\headedsection
{\href{http://www.openhci.com/}{OpenHCI Workshop: A Student-Initiated Workshop on HCI}}
{Taipei, Taiwan}{

	\headedsubsection
	{Program Chair}
	{Jan '13 -- Jul '13}
	{\bodytext{Organize OpenHCI '13 (the 4th OpenHCI Workshop), 
               with 20+ graduate students across department of computer science, design, and communication of three universities}}

	\headedsubsection
	{Director of Human Resources Affair}
	{Jan '11 -- Jul '11}
	{\bodytext{Manage the human resources of OpenHCI '11 (the 2nd OpenHCI Workshop), 
               including attendee registration and volunteer recruitment}}

}

%--- iAgent Lab ----------------------------------------------------------------------------------------------------------%

\headedsection
{\href{http://agent.csie.ntu.edu.tw/}{Intelligent Agents Lab}, 
 \href{http://www.csie.ntu.edu.tw}{Dept. CSIE},
 \href{http://www.ntu.edu.tw}{Natl. Taiwan Univ.}}
{Taipei, Taiwan}{

	\headedsubsection
	{System Administrator}
	{Mar '11 -- Jul '13}
	{\bodytext{Manage devices and web services for 30+ lab members}}

}

%--- StarRain ----------------------------------------------------------------------------------------------------------%

\spacedhrule{1.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after


%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\roottitle{TEACHING EXPERIENCE} % Top level section

\headedsection
{
 \href{http://www.csie.ntu.edu.tw}{Dept. CSIE},
 \href{http://www.ntu.edu.tw}{Natl. Taiwan Univ.} \&
 \href{http://www.dt.ntust.edu.tw/}{Dept. Indst. Design},
 \href{http://www.ntust.edu.tw}{Natl. Taiwan Univ. of Sci. and Tech.}\\
 ``Advanced Human-Computer Interface/User-Oriented Innovation Design''
}
{Taipei, Taiwan}{
	\headedsubsection
	{Teaching Assistant}
	{Feb '13 -- Jun '13}
	{\bodytext{
		Facilitate a cross-campus and interdisciplinary course for graduate students, 
        enrolled by 10+ computer science students and 10+ design students
		}
	}
}

\headedsection
{
 \href{http://www.opehci.com/2011/}{OpenHCI '11}
}
{Taipei, Taiwan}{
	\headedsubsection
	{Team Coach}
	{Jul '11}
	{\bodytext{
		Guide an inter-disciplinary team with six members to complete an interactive design project in the 5-day workshop
		}
	}
}

\headedsection
{
 \href{http://www.csie.ntu.edu.tw}{Dept. CSIE},
 \href{http://www.ntu.edu.tw}{Natl. Taiwan Univ.}\\
 ``Introduction to Computer Science''
}
{Taipei, Taiwan}{
	\headedsubsection
	{Teaching Assistant}
	{Sep '10 -- Jan '11}
	{\bodytext{
		Facilitate an introductory course for 60+ computer science major freshman, and lead studios every other week
		}
	}
}


\spacedhrule{1.5em}{-1em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\roottitle{VOLUNTEER EXPERIENCE} % Top level section

\headedsection
{\href{http://goo.gl/2Dmqrj}{StarRain Service Association for Autism}}
{Taipei, Taiwan}{

	\headedsubsection
	{Volunteer for Autism} 
	{Feb '08 -- Present}
	{\bodytext{Organize and attend volunteer activities for autistic children and teenagers regularly}}

	\headedsubsection
	{Publicist} 
	{Sep '08 -- Jun '09}
	{\bodytext{Publish 4 seasonal magazines and design public relations activities on caring autism}} 
}


\end{document}
